{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-05-30 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

        \subsection{Hoffman error bound and Q-SCNVX}

@@

        \subsection{Application, KKT of linear programming}
            This section extends ideas in the discussion section of Necoara et al. \cite{necoara_linear_2019}. 

@@

                    + (E_1E_1^T)z

@@

                    -bc_1^T& -bc_2^T & E_2E_2^T + E_1E_1^T + bb^T & E_1E_1^T \\
                    & & E_1^Ty & I_{n_1}\\

@@

            Let $f(v) = (1/2)\Vert Av - d\Vert^2$ to be the objective function of optimization problem \eqref{problem:lp-kkt-min}. 
            Its gradient, objective value, and Bregman Divergence have: 
                \nabla f(v) &= A^TAv - A^Td, 
                f(v) &= 
                \frac{1}{2}\langle v, \nabla f(v) - A^Td\rangle + \frac{1}{2}\Vert d\Vert^2, 
                D_f(u, v) &= (1/2)\langle u - v, A^TA (u - v)\rangle
                &= (1/2)\langle \nabla f(u) - \nabla f(v), u - v\rangle. 
            The value $\nabla f(v), f(v)$ when evaluated together, require minimal additional computations. 
            This fact is favorable for implementations in practice. 
            Furthermore, the difference of the function value between 2 points $v, u$ admits an interesting relation via the Bregman Divergence. 
            Observe that $\forall u, v \in \RR^n$ it has 
                f(u) - f(v) &= \langle \nabla f(v), u - v \rangle + D_f(u, v)
                &= \langle \nabla f(v), u - v \rangle + (1/2)\langle \nabla f(u) - \nabla f(v), u - v\rangle
                &= (1/2)\langle \nabla f(u) + \nabla f(v), u - v\rangle. 
            For this problem, the computation overhead for $f(u) - f(v), D_f(u, v)$ is very little if $\nabla f(u), \nabla f(v)$ is known.

>>>>

@@

\chapter{Application, KKT of linear programming}
    This chapter extends ideas by the end of Necoara et al.'s paper \cite{necoara_linear_2019}. 
    \section{Introductions and problem formulations}

@@

                + E_1z

@@

                -bc_1^T& -bc_2^T & E_2E_2^T + E_1E_1^T + bb^T & E_1 \\
                & & E_1^T & I_{n_1}\\

@@

        \subsection{Investigating the matrix}

        \subsection{Speedy evaluations}
            Let $f(v) = (1/2)\Vert Av - d\Vert^2$ to be the objective function of optimization problem \eqref{problem:lp-kkt-min}. 
            Its gradient, objective value, and Bregman Divergence have: 
            \begin{align*}
                \nabla f(v) &= A^TAv - A^Td, 
                \\
                f(v) &= 
                \frac{1}{2}\langle v, \nabla f(v) - A^Td\rangle + \frac{1}{2}\Vert d\Vert^2, 
                \\
                D_f(u, v) &= (1/2)\langle u - v, A^TA (u - v)\rangle
                \\
                &= (1/2)\langle \nabla f(u) - \nabla f(v), u - v\rangle. 
            \end{align*}
            The value $\nabla f(v), f(v)$ when evaluated together, require minimal additional computations. 
            This fact is favorable for implementations in practice. 
            Furthermore, the difference of the function value between 2 points $v, u$ admits an interesting relation via the Bregman Divergence. 
            Observe that $\forall u, v \in \RR^n$ it has 
            \begin{align*}
                f(u) - f(v) &= \langle \nabla f(v), u - v \rangle + D_f(u, v)
                \\
                &= \langle \nabla f(v), u - v \rangle + (1/2)\langle \nabla f(u) - \nabla f(v), u - v\rangle
                \\
                &= (1/2)\langle \nabla f(u) + \nabla f(v), u - v\rangle. 
            \end{align*}
            For this problem, the computation overhead for $f(u) - f(v), D_f(u, v)$ is very little if $\nabla f(u), \nabla f(v)$ is known. 
    \section{Hoffman error bound and Q-SCNVX}
